SDR enhancement by clouds

### 2024-04-07 article/article.tex
Commit 2024-04-06 18:14
Commit 2024-04-07 21:13

\title{SDR enhancement by clouds}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A Short Subtitle}
\author{Athanasios N. Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
\date{2024-04-06}

@@

\(\text{GHI}_\text{mCSi}\): modeled clear sky one minute global horizontal irradiance

@@

For completeness, we will describe here the main points of the radiation simulation
procedure. We used as input the spectrum of Kurucz (1994) in the range \(280\) to
\(2500\,\text{nm}\), with the Libradtran radiation transfer solver ``disort'' on a
``pseudospherical'' geometry and the ``LOWTRAN'' gas parameterization. For each
combination of conditions we use a SZA step of \(0.2^\circ\).
For the atmospheric characteristics, we iterated for combinations of AOD at
\(500\,\text{nm}\) (\(\tau_{500\text{nm}}\)) with additional offsets of \(\pm1\) and
\(\pm2\sigma\), and water column (\(w_h\)), also with offsets of \(\pm1\) and \(\pm2\sigma\).
We applied them on two atmospheric profiles, from the Air Force Geophysics
Laboratory (AFGL). The ``AFGL atmospheric constituent profile, midlatitude summer''
(afglms) and the ``AFGL atmospheric constituent profile, midlatitude winter'' (afglmw)
(Anderson et al. 1986).

To create a look-up table that aligns with our dataset, we applied some adjustments.
To account for the Sun's variability in our one-minute GHI measurements, we corrected
the model's input spectrum integral, to the one of the total solar irradiance (TSI)
provided by NOAA (Coddington et al. 2005). Also, we applied the effect of the Earth -- Sun
distance on the irradiance, by using the distance calculated by the Astropy
(Astropy Collaboration et al. 2022) software library. As needed, we interpolate the resulting
irradiances to the exact SZA of our measurements. For each period of the year, we
used the appropriate atmospheric profile (afglms or afglmw). Finally, we calculated
the clear sky irradiance value at the horizontal plane. Thus, we were able to
emulate different atmospheric condition and levels of atmospheric clearness for the
climatological conditions of the site. With this method, the modeled clear sky
irradiances can be directly compared to each measured one-minute value of GHI, for
different conditions of atmospheric clearness.

@@

After evaluating the modeled clear radiation for the different atmospheric
conditions, in relation to the measured GHI data, we choose as a representative of
the clear sky radiation, the case where
\(\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma\) and \(w_{h\text{cs}} = w_h - 1\sigma\)
(\(\text{GHI}_\text{mCSi}\)).
These values represent a typical atmosphere in Thessaloniki with low load of aerosols
and humidity, which are the main factor that attenuate the GHI, excluding clouds. To
create the limit of CE identification, we created a two branched threshold, as a
function of SZA. A constant factor for low SZAs, and a higher ramped factor for
higher SZAs (Equation\nobreakspace\ref{eq:CE4}).
This is the criterion of our CE identification.
\begin{equation}
\text{CE} : \text{GHI}_\text{i} > \text{GHI}_\text{CSlim,i}, \text{where} \begin{cases}
 \text{GHI}_\text{CSlim,i} = 1.05 \cdot \text{GHI}_\text{mCSi}, & \text{$\theta \leq 60^\circ$}\\
\text{GHI}_\text{CSlim,i} = \left ({ 1.18 + \frac{1.05 - 1.18}{60 - 78} \cdot (\theta- 78) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ 78^\circ > \theta > 60^\circ$}\\
\text{Excluded measurements}, & \theta > 78^\circ
\end{cases}\label{eq:CE4}
\end{equation}
where: \(\theta\) is the solar zenith angle, \(\text{GHI}_\text{i}\) the measured
irradiance, and \(\text{GHI}_\text{mCSi}\) the selected modeled clear sky irradiance.

@@

Another aspect of the CE events, that is often reported in the relative bibliography,
are cases of extreme cloud enhancement (ECE). These are cases of CE where the
measured intensity of the irradiance, exceeds the equivalent TSI on the top of the
atmosphere, and satisfy the Equation\nobreakspace{}\ref{eq:ECE}.
\begin{equation}
\text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times E_{i\odot} / r_{i}^2
\label{eq:ECE}
\end{equation}
where: \(\theta\) the solar zenith angle, \(E_{\odot}\) the solar constant, \(r\) the Sun -- Earth distance, \(i\) each of the one-minute observation

@@

\begin{itemize}
\tightlist
\item
  Include Example of days plot in the Appendix?
  \ldots{} this is clearer to understand and describe \ldots.
\end{itemize}

@@

Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one-minute measurements. The annual
mean OIR is
\(0.23\pm 0.11\,W/m^2/y\)
(Figure\nobreakspace{}\ref{fig:P-energy-mean}),
but this value alone is not very useful due the intrinsic high variability of this
metric.

@@

Subsequently, the total annual energy observed during CE events shows an increase of
\(341.6\pm 73.1\,kJ/y\)
(Figure~\ref{fig:P-energy-sum}), witch follows the trend of the number of
occurrences.

>>>>

\title{SDR enhancement by clouds}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A Short Subtitle}
\author{Athanasios N. Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
\date{2024-04-07}

@@

\(\text{GHI}_\text{CSm}\): modeled clear sky one minute global horizontal irradiance

@@

For completeness, we will describe here the main points of the radiation simulation
procedure. We used as input the spectrum of Kurucz (1994) in the range \(280\) to
\(2500\,\text{nm}\), with the Libradtran radiation transfer solver ``disort'' on a
``pseudospherical'' geometry and the ``LOWTRAN'' gas parameterization. For each
combination of conditions we use a SZA step of \(0.2^\circ\).
For the atmospheric characteristics, we iterated for combinations of AOD at
\(500\,\text{nm}\) (\(\tau_{500\text{nm}}\)) with additional offsets of \(\pm1\) and
\(\pm2\sigma\), and water column (\(wc\)), also with offsets of \(\pm1\) and \(\pm2\sigma\).
We applied them on two atmospheric profiles, from the Air Force Geophysics
Laboratory (AFGL). The ``AFGL atmospheric constituent profile, midlatitude summer''
(afglms) and the ``AFGL atmospheric constituent profile, midlatitude winter'' (afglmw)
(Anderson et al. 1986).

To create a look-up table that aligns with our dataset, we applied some adjustments.
To account for the Sun's variability, in our one-minute GHI measurements,
we adapted each modeled value by scaling the\\
model's input spectrum integral, to the corresponding total solar irradiance (TSI)
provided by NOAA (Coddington et al. 2005).\\
Also, we applied the effect of the Earth -- Sun
distance on the irradiance, by using the distance calculated by the Astropy
(Astropy Collaboration et al. 2022) software library. As needed, we interpolate the resulting
irradiances to the exact SZA of our measurements. For each period of the year, we
used the appropriate atmospheric profile (afglms or afglmw). Finally, we calculated
the clear sky irradiance value at the horizontal plane. Thus, we were able to
emulate different atmospheric condition and levels of atmospheric clearness for the
climatological conditions of the site. With this method, the modeled clear sky
irradiances can be directly compared to each measured one-minute value of GHI, for
different conditions of atmospheric clearness.

@@

After evaluating the modeled clear radiation for the different atmospheric
conditions, in relation to the measured GHI data, we choose as a representative of
the clear sky radiation, the case where
\(\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma\) and \(w_{h\text{cs}} = w_h - 1\sigma\)
(\(\text{GHI}_\text{CSm}\)).
These values represent a typical atmosphere in Thessaloniki with low load of aerosols
and humidity, which are the main factor that attenuate the GHI, excluding clouds. To
create the limit of CE identification, we created a two branched threshold, as a
function of SZA. A constant factor for low SZAs, and a higher ramped factor for
higher SZAs (Equation\nobreakspace\ref{eq:CE4}).
This is the criterion of our CE identification.
\begin{equation}
\text{CE} : \text{E}_\text{i} > \text{E}_\text{CSlim,i}, \text{where} \begin{cases}
 \text{E}_\text{CSlim,i} = 1.05 \cdot \text{E}_\text{CSm,i}, & \text{$\theta \leq 60^\circ$}\\
\text{E}_\text{CSlim,i} = \left ({ 1.18 + \frac{1.05 - 1.18}{60 - 78} \cdot (\theta- 78) } \right ) \cdot \text{E}_\text{CSm,i}, & \text{$ 78^\circ > \theta > 60^\circ$}\\
\text{Excluded measurements}, & \theta > 78^\circ
\end{cases}\label{eq:CE4}
\end{equation}
where: \(\theta\) is the solar zenith angle, \(\text{E}\) the measured
irradiance, \(\text{E}_\text{CSm}\) the selected modeled clear sky irradiance, and \(i\) each of the one-minute observation.

@@

Another aspect of the CE events, that is often reported in the relative bibliography,
are cases of extreme cloud enhancement (ECE). These are cases of CE where the
measured intensity of the irradiance, exceeds the equivalent TSI on the top of the
atmosphere, and satisfy the Equation\nobreakspace{}\ref{eq:ECE}.
\begin{equation}
\text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times E_{i\odot} / r_{i}^2
\label{eq:ECE}
\end{equation}
where: \(\theta\) the solar zenith angle, \(E_{\odot}\) the solar constant, \(r\) the Sun -- Earth distance, and \(i\) each of the one-minute observation.

@@

\begin{itemize}
\tightlist
\item
  Include Example of days plot in the Appendix!
  \ldots{} this is clearer to understand and describe \ldots.
\end{itemize}

@@

Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one-minute measurements. The trend of
OIR is
\(0.23\pm 0.11\,W/m^2/y\)
(Figure\nobreakspace{}\ref{fig:P-energy-mean}),
but this value alone is not very useful due the intrinsic high variability of this
metric.

@@

Subsequently, the mean annual increase of energy due to CE events is
\(341.6\pm 73.1\,kJ/y\)
(Figure~\ref{fig:P-energy-sum}), witch follows the trend of the number of
occurrences.
